Death License Registrations May Indicate a Discrepency in Reported Data During the COVID-19 Pandemic

### 2023-02-04 outputs/paper/paper.qmd
Updated title

---
title: "Death License Registrations May Indicate a Discreptency in Reported Data During the COVID-19 Pandemic"
subtitle: "An Analysis of Death License Registrations in Toronto from 2016-2020"
author: "Chloe Thierstein"
thanks: "Code and data are available at: https://github.com/cthierst/death_registry_analysis.git."
date: "February 3, 2023"
date-format: "D MMMM YYYY"
format: 
  pdf:
    documentclass: article
    geometry: margin = 1in
    abstract:  "Death registry statistics offer us a useful tool to better out healthcare system, from monitoring trends to government policy, it is essential to our understanding of the world around us. The COVID-19 pandemic marked a significant shift in the Canadian mortality rate in the year 2020. This paper utilizes death registry data from three civic centres in the greater Toronto area from 2016 to 2020, alongside secondary sources and research. From this work, we demonstrate that even data from considerably reliable sources may become distorted if enough care is not taken in its recording and the world around the data is not considered."
bibliography: references.bib
fig-cap-location: top
---

>>>>

---
title: "Death License Registrations May Indicate a Discrepency in Reported Data During the COVID-19 Pandemic"
subtitle: "An Analysis of Death License Registrations in Toronto from 2016-2020"
author: "Chloe Thierstein"
thanks: "Code and data are available at: https://github.com/cthierst/death_registry_analysis.git."
date: "February 3, 2023"
date-format: "D MMMM YYYY"
format: 
  pdf:
    documentclass: article
    geometry: margin = 1in
    abstract:  "Death registry statistics offer us a useful tool to better out healthcare system, from monitoring trends to government policy, it is essential to our understanding of the world around us. The COVID-19 pandemic marked a significant shift in the Canadian mortality rate in the year 2020. This paper utilizes death registry data from three civic centres in the greater Toronto area from 2016 to 2020, alongside secondary sources and research. From this work, we demonstrate that even data from considerably reliable sources may become distorted if enough care is not taken in its recording and the world around the data is not considered."
bibliography: references.bib
fig-cap-location: top
---
